|

### 2020-09-14 paper.Rmd
remove prints

mouse <- draw_panel(mouse_grand_panel, mouse_sage_panel)
print(mouse)
```

@@

sketches <- draw_panel(sketches_grand_panel, sketches_sage_panel)
print(sketches)
```

@@

pdfsense <- draw_panel(pdfsense_grand_panel, pdfsense_sage_panel)
print(pdfsense)
```

>>>>

mouse <- draw_panel(mouse_grand_panel, mouse_sage_panel)
mouse
```

@@

sketches <- draw_panel(sketches_grand_panel, sketches_sage_panel)
sketches
```

@@

pdfsense <- draw_panel(pdfsense_grand_panel, pdfsense_sage_panel)
pdfsense
```
